Biden Expected to Win 54% of Popular Vote in 2020 US Presidential Election

### 2020-11-03 outputs/paper/paper.Rmd
Fix bib.
added greater budget

# Results
We will go over our cross validation results, the most significant

@@

>>>>

# Results
We will go over our cross validation results, the explanatory variables that have the largest impact on the response variable, and post-stratification predictions.

@@

If we had the ability to allocate a greater budget to polling companies, we assuredly could achieve a better estimate. The key improvement would be to ask more people and ask more questions, such as religion. With a greater number of questions we could subsequently create more cells to work with, and with increasing the range of respondents stratification can occur.
